Improving Item-Item Similarity Estimation during Collaborative Filtering

### 2014-03-24 paper/paper.tex
Add opening paragraph.

\section*{Introduction}
The similarity of two items is a valuable measurement for a number of
data-mining applications, such as recommender systems. With large amounts of
rating data, collaborative filtering is a good method for calculating
similarity. However, with sparse rating data, this technique gives noisy and
unreliable approximations for similarity. Even worse, low confidence
measurements of similarity are indistinguishable from high confidence ones. In
this paper, we develop and compare a number of methods to produce more accurate
estimates of similarity by incorporating confidence into the similarity score.

>>>>

\section*{Introduction}
Accurate estimations of the similarity of two users or items is valuable for a
number of data-mining applications including recommender systems, product
assortment and differentiation, as well as branding. Collaborative filtering is
often used to exploit user-item rating data to make such estimates typically by
computing the Pearson correlation or cosine similarity of vector representations
of the users or items \cite{Breese98}. Given sufficient user-item rating data,
this approach can be very effective. On the otherhand, when very little rating
data for one or both users/items is available, unmodified, these metrics can
yield dramatic discrepancies compared to values computed later once sufficient
data has been acquired. In this report, we describe two novel techniques for
estimating the true similarity of two users or items given limited common rating
data.

.....

Even worse, low confidence measurements of similarity are indistinguishable from
high confidence ones. In this paper, we develop and compare a number of methods
to produce more accurate estimates of similarity by incorporating confidence
into the similarity score.
